Robust Bayesian Analysis of Causal Inference Problems

### 2024-03-22 JASA-template.tex
Small rephrasing.
Some updates, question about bounds for mathcal{P}.

For the simulation studies, we consider 2 different settings. In each
case, we generate the design matrix $X$ such that $X_i\sim\mathcal{N}(0, \Sigma)$
for $1\le i\le n$ where $\Sigma_{ij} = 0.3^{|i-j|}$. In this way, we 
generate 50 predictors for our model with mild correlations among them.
We then use the following distributions to generate the outcome and
the treatment indicator: 
\begin{equation}
    T_i \sim \text{Bernoulli}\left(1/(1+\exp(-X_i\gamma))\right)
    \quad\text{and}\quad
    Y_i = 4T_i + X_i\beta.
\end{equation}
\begin{description}
    \item[Scenario 1] --- $|\gamma_j|, |\beta_j|>0$ for $j\le 10$
    \item[Scenario 2] --- $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$
\end{description}
For both
the cases, we consider different numbers of observations $n$ where
$n=25+ 5k$ for $k=0,1,2,\dots,10$.

We present our analyses in \cref{tab:causal,tab:misspec}.
For the sake of clarity we use the following accronyms: RBCE for 
robust Bayesian causal estimation (our method); SSCE for spike and
slab causal estimation \cite{koch2020}; BSSCE for bi-level spike and slab causal
estimation \cite{koch2020}; and BSSL for Bayesian spike and slab LASSO
\cite{xu2015}. As it can be
seen from both the tables, SSCE and BSSCE are formulated for problems
where $p\le n$ and therefore we do not have any results for $n<50$.

\paragraph{Elicitation} For the
elicitation of $\mathcal{P}$, we use marginal correlation between 
$Y$ and $X$ to determine the bounds on number of active variables. We 
set the thresholds to be $0.15$ and $0.35$ for the correlations. We compute the
number of variables with marginal correlation greater than 0.15
(say $p_1$) and number of variables with  marginal 
correlation greater than 0.35 (say $p_2$). 
We use these numbers to obtain the bounds on the number of active
variables so that $\mathcal{P}=[p_2/p , p_1/p]$.

@@

\paragraph{Results}
We provide our result for causal estimate in \cref{tab:causal}. 
As we perform a sensitivity analysis,
our method gives an interval estimate for the causal effect and we show
that in two different rows where the first row gives the lower bound
and the second row gives the upper bound. We notice that our method is 
somewhat in agreement with the other methods but much more consistent
in terms of estimating the treatment effect. However, this is not the
case for other methods and sometimes those methods produce extreme 
values. This can be observed in \cref{fig:comp:trt} as well. Here, the true 
value is represented by the straight line for $\beta_T = 4$.

>>>>

For the simulation studies, we consider 2 different settings. In each
case, we generate the design matrix $X$ such that $X_i\sim\mathcal{N}(0, \Sigma)$
for $1\le i\le n$ where $\Sigma_{ij} = 0.3^{|i-j|}$. In this way, we 
generate 50 predictors for our model with mild correlations among them.
We then use the following distributions to generate the outcome and
the treatment indicator: 
\begin{equation}
    T_i \sim \text{Bernoulli}\left(1/(1+\exp(-X_i\gamma))\right)
    \quad\text{and}\quad
    Y_i = 4T_i + X_i\beta.
\end{equation}
%%% MT to BT: added this sentence for clarity later when discussing tables
Note that the simulated causal effect $\beta_T$ is equal to $4$.
\begin{description}
    \item[Scenario 1] --- $|\gamma_j|, |\beta_j|>0$ for $j\le 10$
    \item[Scenario 2] --- $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$
\end{description}
For both
the cases, we consider different numbers of observations $n$ where
$n=25+ 5k$ for $k=0,1,2,\dots,10$.

We present our analyses in \cref{tab:causal,tab:misspec}.
For the sake of clarity we use the following accronyms: RBCE for 
robust Bayesian causal estimation (our method); SSCE for spike and
slab causal estimation \cite{koch2020}; BSSCE for bi-level spike and slab causal
estimation \cite{koch2020}; and BSSL for Bayesian spike and slab LASSO
\cite{xu2015}. Note that since SSCE and BSSCE are formulated for problems
where $p\le n$, we do not have any results for $n<50$ for these cases.

\paragraph{Elicitation}
For the
elicitation of $\mathcal{P}$, we use the marginal correlation between 
$Y$ and $X$ to determine bounds on the number of active variables.
%%% MT to BT: I think we need to clarify what is going on here... What
%%% were the marginal correlations? How are these values 0.15 and 0.35
%%% informed from the marginal correlations? Also, why are marginal
%%% correlations the best way to do this? Ideally, one would set this
%%% without reference to the data... (since it is prior elicitation)
We set the thresholds to be $0.15$ and $0.35$ for the correlations.
We compute the
number of variables with marginal correlation greater than 0.15
(say $p_1$) and number of variables with  marginal 
correlation greater than 0.35 (say $p_2$). 
We use these numbers to obtain the bounds on the number of active
variables so that $\mathcal{P}=[p_2/p , p_1/p]$.

@@

\paragraph{Results}
\Cref{tab:causal} shows the results of estimating the causal effect $\beta_T$. 
As we perform a sensitivity analysis,
our method gives an interval estimate for the causal effect and we show
that in two different rows where the first row gives the lower bound
and the second row gives the upper bound. We notice that our method is 
somewhat in agreement with the other methods but much more consistent
in terms of estimating the treatment effect. However, this is not the
case for other methods and sometimes those methods produce extreme 
values. This can be observed in \cref{fig:comp:trt} as well. Here, the true 
value is represented by the straight line for $\beta_T = 4$.
